Short_note_captured_phenotype

### 2024-12-09 Short_note_captured_phenotype_journal_version.qmd
Update libraries

```{r loading used packages and functions}
library(stringr)#gestion chaines de caractères
library(car)#anova ou graph d'analyse
library(RVAideMemoire)#variance
library(corrplot)# graphe correlation
library(ggeffects) #effet prédit
library(ggplot2) #graphs
library(ggtext) #customization of ggplot legends
library(ggpubr) #custom graph (comparison bars)

library(multcomp) #multiple comparison of contrasts

library(data.table) #large dataset gestion

library(lme4) #mixed model
library(blme) #bayesian mixed model (handling singular fit)
library(DHARMa) #model diagnostic (mixed models/non linear models)
library(MuMIn) #r-squared for glmm (Nakagawa method)
library(rsq) #diverse rsquared including Nagelkerke

@@

library(sf) #spatial treatments

@@

library(MASS) #used to generate multivariate normal distribution

@@

sumna <- function(x) {
    ret <- sum(x, na.rm = TRUE)
    if(ret == 0 && all(is.na(x))) {NA_real_} else {ret}
}

@@

ggplot(OBSMER_Bycatch[!is.na(BODY_LENGTH) & SPECIES == "Delphinus delphis",], aes(BODY_LENGTH, SEA_STATE_grouped)) + geom_violin() + geom_boxplot(width = 0.1) +  stat_compare_means(label = "p.format", comparisons = list(c("2 - belle, vagues de 0.1 à 0.5 mètres", "Calme ou ridée"), c("3 - peu agitée, vagues de 0.5 à 1.25 mètres", "Calme ou ridée"), c("4 - agitée, vagues de 1.25 à 2.5 mètres", "2 - belle, vagues de 0.1 à 0.5 mètres"), c("Forte à grosse", "Calme ou ridée")), size=9) + ggtitle("Common dolphin - BL model - OBSMER dataset") +  labs(y = "Sea conditions (Douglas scale)", x = "Captured individuals' body length (cm)") +  theme(text = element_text(size = 30)) + scale_y_discrete(labels=c("Calm (0-1)", "Smooth (2)", "Slight (3)", "Moderate (4)", "Rough (>5)"))

@@

setDT(TableS7)
TableS7[, lapply(.SD, function(x) ifelse(str_detect(x, "\n"), str_replace_all(x, "\n", " "), x))]
setDF(TableS7)

 kable_classic(collapse_rows(kbl(TableS7, format = "latex"), columns = 1:2, target = 1, valign= "middle"))

>>>>

```{r loading used packages and functions}
library(stringr)# handling string format in R 
library(car) # Anova analysis
library(ggeffects) # prediction of effects from regression models
library(ggplot2) #graphs
library(ggtext) #customization of ggplot legends
library(ggpubr) #custom graph (comparison bars)

library(data.table) #large dataset handling

library(lme4) #mixed regression models
library(DHARMa) #model diagnostic (mixed models/non linear models)
library(rsq) #diverse rsquared including Nagelkerke

@@

library(sf) #spatial operations

@@

@@

@@

ggplot(OBSMER_Bycatch[!is.na(BODY_LENGTH) & SPECIES == "Delphinus delphis",], aes(BODY_LENGTH, SEA_STATE_grouped)) + 
  geom_violin() + geom_boxplot(width = 0.1) +
  stat_compare_means(label = "p.format", comparisons = list(c("2 - Smooth", "0, 1 - Calm"), c("3 - Slight", "0, 1 - Calm"), c("4 - Moderate", "2 - Smooth"), c("5, 6 - Rough to very rough", "0, 1 - Calm")), size=9) + 
  ggtitle("Common dolphin - BL model - OBSMER dataset") +
  labs(y = "Sea conditions (Douglas scale)", x = "Captured individuals' body length (cm)") +  theme(text = element_text(size = 30)) + scale_y_discrete(labels=c("Calm (0-1)", "Smooth (2)", "Slight (3)", "Moderate (4)", "Rough (>5)"))

@@

setDT(TableS7)
TableS7 = TableS7[, lapply(.SD, function(x) ifelse(str_detect(x, "\n"), str_replace_all(x, "\n", " "), x))]
setDF(TableS7)

 kable_classic(collapse_rows(kbl(TableS7, format = "latex"), columns = 1:2, target = 1, valign = "middle"))
